DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-06 scnn.tex
point to the zenodo repository

The performance of DeepSphere is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters (see \secref{data} for details).
The classification methods were trained to predict a label from a HEALPix map.
Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
The data is available upon request from the cosmology group.\footnote{\url{http://www.cosmology.ethz.ch}}

>>>>

The performance of DeepSphere is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters (see \secref{data} for details).
The classification methods were trained to predict a label from a HEALPix map.
Our Python implementation to reproduce those experiments is openly available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}}
The data is available upon request.\footnote{\url{https://doi.org/10.5281/zenodo.1303272}}
